p-CAPTCHAs and the Recognition Problem

### 2012-02-17 frostedglass/paper.tex
Added a section about general considerations.
q

\begin{document}
\title{p-CAPTCHAs and the Recognition Problem}
\author{Ben Warner}
\maketitle

@@

\section*{Introduction}
Modern cryptosystems combine a publicly available encryption algorithm with one or more secret keys in order to convert a computer or human readable message (plaintext) into data that cannot be read by a computer or human (ciphertext). Typically, the encryption and decryptions algorithms are publically available, but are designed so that only possessors of the decryption key are able to use the decryption algorithm to read the message. Cryptosystems such as the Advanced Encryption Standard (AES) put the bits of the message file through a series of substitutions and permutations until the ciphertext becomes apparently random, so that analyzing statistical properties of the ciphertext do not reveal enough information to obtain the plaintext without possessing the decryption key. (In AES, encryption and decryption are performed using the same key, but we are assuming an attacker does not possess it.)

One well known way of attacking a cryptosystem is to employ a brute-force attack, that is, to use a computer to systematically try every key in the decryption key space (set of possible decryption keys). In order to make the brute-force attack infeasible, cryptosystems such as AES use large key spaces (128-bit keys or larger) so that there will be too many potential keys to search through in any reasonable amount of time. However, the brute-force attack may succeed if an attacker has access to greater computing resources. Advances in hardware technology allowed the Digital Encryption Standard (DES) to be broken in the late 1990s by means of a brute-force attack. (DES only used 56-bit keys.)

@@

Laptyeva et al. present a technique to resist a brute-force attack even when the decryption key space is small \cite{laptyeva}. Their approach is to focus on increasing the difficulty of the recognition problem through the use of a Completely Automated Public Turing test to tell Computers and Humans Apart (CAPTCHA). In Laptyeva et al's system, the encryption key (EK) (which is also used as the decryption key) is the sum of a short password (SP) that the user memorizes, and a strong key (SK) that the computer provides. SK is text in the form of a hard to recognize CAPTCHA-ized image, which they call a p-CAPTCHA, the "p" in front because it is a CAPTCHA of a password. The image of SK is not stored on the computer, but rather a transformed version of it. This CAPTCHA-ized SK is considered to be the plaintext, and the transformed version of it the ciphertext. In order to obtain the image of SK, the user types in SP which the computer uses to run the transformation process in reverse to obtain the image of SK. At this point, the computer shows the image of SK to a human who then types it in.

@@

Laptyeva et al. spend much of their paper describing the transformation process on SK, but devote very little space explaining why the computer will have difficulty differentiating a true image of SK, as produced by the correct SP, from a spurious one obtained from the wrong SP, yet the strength of the system depends on the difficulty of solving this recognition problem. The remainder of this paper will be devoted to a discussion of metrics related to solving a recognition problem, and the presentation of another p-CAPTCHA system.

@@

This suggests that the objective of a p-CAPTCHA “cryptanalysis” is to identify a small subset of potentially correct candidate images to show to a human user. One way to do this would be to have a function that takes in every image and creates a score based on how likely it is that the image being viewed is the true image (the plaintext). With each candidate image having a score, the candidates can be sorted and then the computer can either try to read the CAPTCHA directly and enter the password, or the images can be shown to a human user in order of most likely (according to the computer's judgement) to be the plaintext.

@@

Dividing both sides of the last inequality by $n_{sp}$, we get system security when $\frac{n_f}{n_{SP}} < F(l)$. This could be accomplished by increasing $n_{SP}$, but if we could increase the size of our key space, we may as well use a traditional symmetric-key cryptosystem like AES. Thus, a p-CAPTCHA system is valuable when $n_{SP}$ is small and cannot be increased. We are trying to make the recognition problem sufficiently difficult that $F(l)$ is large. Because we are designing $R$ to give a lower score to $CI_{true)$, $F(l)$ will be largest when the distribution of $X_k$ is close to the distribution of $Y$, or in other words, when $R$ mistakenly assigns low scores to false candidate plaintexts because they look a lot like the true plaintext. This metric can be applied to any approach that attempts to recognize a true plaintext from a false one by minimizing some measurement of each candidate image, whether this is being applied to the p-CAPTCHA system presented by Laptyeva et al., the one presented below, or another approach. A framework similar to this could be applied to an attack that maximizes some measurement of each candidate image.

@@

CAPTCHAs are sometimes broken so it is worthwhile to have ideas of different approaches. Similarly, it is valuable to learn about more possible ways of creating p-CAPTCHAs in case one of them is broken.

@@

%If the computer cannot solve the recognition problem but can read still read the CAPTCHA plaintext (obtaining spurious strong keys from false candidate images) then it will nevertheless have SK which puts it a lot closer to obtaining EK.

%Don't turn your OCR problem into a simple math problem.

%If the computer can identify part but not all of the plaintext from a spurious image, then it may provide enough information to reduce the size of the strong key space so that the computer can mount a brute-force attack directly on the strong key.

%A good CAPTCHA is not enough. A p-CAPTCHA system must contain both a CAPTCHA and a recognition problem.

\subsection*{Fuzzy Letter Tiles}
	Another p-CAPTCHA encryption method involves rearranging tiles of hard to recognize “fuzzy” letters. An example of this method is given in Figure~{\ref{EncryptionProcess}}. First, a strong key (SK) is written as an image with warped and randomly offset letters. Second, random pixels are XORed between black and white to remove the presence of well-defined edges. Third, the image is partitioned into tiles. Fourth, the tiles are rearranged according to a permutation identified by the short password (SP).

@@

The p-CAPTCHA plaintext in Figure~{\ref{EncryptionProcess}} encrypted by permuting 57 blocks. Although there are 57-factorial permutations of 57 blocks, most of these permutations are irrelevant. Each permutation must be tied to a decryption key in order for it to be found by the user. Since we are assuming that the decryption algorithm is known, an attacker will only have to deal with as many candidate images as the decryption algorithm will produce from the small decryption key space.

@@

Some parameters of this system could be adjusted, such as the size of the letters, the amount of fuzziness (noise) in the background and in the letters, and the size of the tiles that get permuted. By adjusting these parameters, we can better position ourselves in the window of possible images that are too difficult for a human to recognize, but still possible for a human to read without confusing the letters.

Some care should be taken when choosing parameters. We do not want our tiles to be so small that permuting them makes the image look like pure noise, with no semblance of letters. We also do not want our tiles to be so large that a good portion of the letter is contained in each tile. While this would make the scrambled plaintext look a lot like the true plaintext, a human could figure out what letters were being used by looking at a scrambled image. By typing these letters into the computer, the computer could then try a brute force attack with permutations of these letters without needing to solve any OCR problem.

>>>>

\begin{document}
\title{p-CAPTCHAs and the Recognition Problem}
%\author{Ben Warner}
\maketitle

@@

\section*{Introduction}
Modern cryptosystems combine a publicly available encryption algorithm with one or more secret keys in order to convert a computer or human readable message (plaintext) into data that cannot be read by a computer or human (ciphertext). Typically, the encryption and decryptions algorithms are publically available, but are designed so that only possessors of the decryption key are able to use the decryption algorithm to read the message. Cryptosystems such as the Advanced Encryption Standard (AES) put the bits of the message file through a series of substitutions and permutations until the ciphertext becomes apparently random, so that analyzing statistical properties of the ciphertext do not reveal enough information to obtain the plaintext without possessing the decryption key.

One well known way of attacking a cryptosystem is to employ a brute-force attack, that is, to use a computer to systematically try every key in the decryption key space (set of possible decryption keys). In order to make the brute-force attack infeasible, AES uses 128-bit keys or larger so that there will be too many potential keys to search through in any reasonable amount of time. However, the brute-force attack may succeed if an attacker has access to greater computing resources. Advances in hardware technology allowed the Digital Encryption Standard (DES) to be broken in the late 1990s by means of a brute-force attack. (DES only used 56-bit keys.)

@@

Laptyeva et al. present a technique to resist a brute-force attack even when the decryption key space is small \cite{laptyeva}. Their approach is to focus on increasing the difficulty of the recognition problem through the use of a Completely Automated Public Turing test to tell Computers and Humans Apart (CAPTCHA). In Laptyeva et al's system, the encryption key (EK) is the sum of a short password (SP) that the user memorizes, and a strong key (SK) that the computer provides. SK is text in the form of a hard to recognize CAPTCHA-ized image, which they call a p-CAPTCHA, the "p" in front because it is a CAPTCHA of a password. The image of SK is not stored on the computer, but rather a transformed version of it. This CAPTCHA-ized SK is considered to be the plaintext, and the transformed version of it the ciphertext. In order to obtain the image of SK, the user types in SP which the computer uses to run the transformation process in reverse to obtain the image of SK. At this point, the computer shows the image of SK to a human who then types it in.

@@

Laptyeva et al. spend much of their paper describing the transformation process on SK, but devote very little space explaining why the computer will have difficulty differentiating a true image of SK, as produced by the correct SP, from a spurious one obtained from the wrong SP, yet the strength of the system depends on the difficulty of solving this recognition problem. The remainder of this paper will be devoted to the presentation of another p-CAPTCHA system and a discussion of metrics related to solving a recognition problem.

@@

This suggests that the objective of a p-CAPTCHA “cryptanalysis” is to identify a small subset of potentially correct candidate images to show to a human user. One way to do this would be to have a function that takes in every image and creates a score based on how likely it is that the image being viewed is the true image (the plaintext). With each candidate image having a score, the candidates can be sorted and then the computer can either try to read the CAPTCHA directly and enter the password, or the images can be shown to a human user in order of most likely, according to the computer's judgement, to be the plaintext.

@@

Dividing both sides of the last inequality by $n_{sp}$, we get system security when $\frac{n_f}{n_{SP}} < F(l)$. This could be accomplished by increasing $n_{SP}$, but if we could increase the size of our key space, we may as well use a traditional symmetric-key cryptosystem like AES. Thus, a p-CAPTCHA system is valuable when $n_{SP}$ is small and cannot be increased. We are trying to make the recognition problem sufficiently difficult that $F(l)$ is large. Because we are designing $R$ to give a lower score to $CI_{true}$, $F(l)$ will be largest when the distribution of $X_k$ is close to the distribution of $Y$, or in other words, when $R$ mistakenly assigns low scores to false candidate plaintexts because they look a lot like the true plaintext. This metric can be applied to any approach that attempts to recognize a true plaintext from a false one by minimizing some measurement of each candidate image, whether this is being applied to the p-CAPTCHA system presented by Laptyeva et al., the one presented below, or another approach. A framework similar to this could be applied to an attack that maximizes some measurement of each candidate image.

@@

CAPTCHAs are sometimes broken so it is worthwhile to have ideas of different approaches. Similarly, it is valuable to learn about more possible ways of creating p-CAPTCHAs in case one of them is broken. Some general things to consider when designing a p-CAPTCHA system:
\begin{itemize}
\item The variety of CAPTCHAs that one can use is smaller when trying to exploit the recognition problem because recognizing a true p-CAPTCHA plaintext will generally be easier than reading a CAPTCHA. (See Figure~{\ref{CAPTCHALevels}}.) One must have a CAPTCHA and a transformation that makes the transformed plaintexts look like the true plaintext.
\item Focus on increasing the difficulty of the recognition problem. If you use your short key to encode a lot of information about parameters, you may have less available to connect to spurious plaintexts. If an attacker could figure out that some combinations of parameters are not possible, any keys tied to those parameters could be immediately eliminated, reducing an already small key space without requiring any OCR.
\item If you are transforming an image of a strong key, be careful that the transformed image does not have recognizable parts of the strong key. For example, if the strong key is ten characters, but four of the characters can be figured out from looking at a transformed image, then at that point it may be feasible to mount a brute-force attack directly on the strong key which now has only six unknown characters.
\end{itemize}

@@

\subsection*{Fuzzy Character Tiles}
	Another p-CAPTCHA encryption method involves rearranging tiles of hard to recognize “fuzzy” characters. An example of this method is given in Figure~{\ref{EncryptionProcess}}. First, a strong key (SK) is written as an image with warped and randomly offset characters. Second, random pixels are XORed between black and white to remove the presence of well-defined edges. Third, the image is partitioned into tiles. Fourth, the tiles are rearranged according to a permutation identified by the short password (SP).

@@

The p-CAPTCHA plaintext in Figure~{\ref{EncryptionProcess}} was encrypted by permuting 57 blocks. Although there are 57-factorial permutations of 57 blocks, most of these permutations are irrelevant. Each permutation must be tied to a decryption key in order for it to be found by the user. Since we are assuming that the decryption algorithm is known, an attacker will only have to deal with as many candidate images as the decryption algorithm will produce from the small decryption key space.

@@

Some parameters of this system could be adjusted, such as the size of the characters, the amount of fuzziness (noise) in the background and in the characters, and the size of the tiles that get permuted. By adjusting these parameters, we can better position ourselves in the window of possible images that are too difficult for a human to recognize, but still possible for a human to read without confusing the characters.

Some care should be taken when choosing parameters. We do not want our tiles to be so small that permuting them makes the image look like pure noise, with no semblance of characters. We also do not want our tiles to be so large that a good portion of the letter is contained in each tile. While this would make the scrambled plaintext look a lot like the true plaintext, a human could figure out what characters were being used by looking at a scrambled image. By entering these characters into the computer, the computer could then try a brute force attack with permutations of these characters without needing to solve any OCR problem.
